IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-10-29 ms.tex
I also added a phase folded time series for 2MASS J0835 side by side with 2MASS J1821.
I put in a few references to early work on variability and models.
I added some more details about the observations, slit, calibration etc.

@@

\begin{table*}
\begin{center}
\begin{tabular}{cccc}
Name & Rotation Period & Spectral Type & K magnitude \\
-- & hr & -- & -- \\
\hline \hline
2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L5 & 11.14 \\
2MASS J0835-019 & 9 & L5 & 11.65 \\
\end{tabular}
\end{center}
\end{table*}

\section{Observations}
We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
For 2MASS J1821, we observed a simultaneous reference - 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24\arcsec.
We were able to measure spectrophotometry over 7.47 hours, which was 1.78 rotations at the rotation period.
Assuming the brown dwarfs cloud structure was relatively unchanged in one rotation, this enabled confirmation that the signal was astrophysical as opposed to the systematics affecting the same instrument telescope for observations of the  KIC 12557548 system \citep{schlawin2016kic1255}.
%Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px
For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
%Using SpeX Guider image for distance of 241px  and plate scale in header of 0.116 arcsec/px

\begin{table*}
\begin{center}
\begin{tabular}{ccccc}
Target & Observing Date & N$_{int}$ & t$_{exp}$ & Reference Star \\
-- & UT Start & -- & (s) & -- \\
\hline
2MASS J1821 & 2015-12-31 & 363 & 45 & 2MASS 18212622+1414064 \\
2MASS J0835 & 2016-06-25 & 352 & 60 & 2MASS 08354383-0819212 \\
\end{tabular}
\end{center}
\end{table*}

@@

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
	\label{fig:specphot0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
	\label{fig:specphot1821}
	}
	\caption{Top Panels: The target stars' median raw spectrum compared with the reference star. The areas near 1.4 and 1.8 $\mu$m are contaminated by telluric water absorption. The reference stars are significantly higher temperatures. Bottom Panels: Dynamic spectrum of 2MASS J1821.}
	\label{fig:corner}
\end{figure*}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
\caption{Time Series.}\label{fig:1821tser}
\end{figure}

>>>>

L dwarfs are found to be variable with periods of 1-100 hours \citep{bailer-jones1999bdvar,bailer-jones1999varevo}.
This variability is explained by a patchy clouds at the L/T transition \citep{marley2010patchyc}.

@@

\begin{table*}
\begin{center}
\begin{tabular}{cccc}
Name & Rotation Period & Spectral Type & K magnitude \\
-- & hr & -- & -- \\
\hline \hline
2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L4.5 & 11.14 \\
2MASS J0835-019 & 9 & L5 & 11.65 \\
\end{tabular}
\end{center}
\end{table*}

\section{Observations}

For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.

We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
For 2MASS J1821, we observed a simultaneous reference - 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24\arcsec.
We were able to measure spectrophotometry over 7.47 hours, which was 1.8 rotations at the 4.2 rotation period from \citet{metchev2015weatherII}.

As visible in Figure \ref{fig:specphot1821}, the light curves repeat the same fluctuations after one rotation period.
Assuming the brown dwarfs cloud structure was relatively unchanged in one rotation, this enabled confirmation that the signal was astrophysical as opposed to the systematics affecting the same instrument telescope for observations of the  KIC 12557548 system \citep{schlawin2016kic1255}.
%Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px

%Using SpeX Guider image for distance of 241px  and plate scale in header of 0.116 arcsec/px

@@

\begin{table*}
\begin{center}
\caption{Observing Parameters}\label{tab:obsParam}
\begin{tabular}{ccccc}
Target & Observing Date & N$_{int}$ & t$_{exp}$ & Reference Star \\
-- & UT Start & -- & (s) & -- \\
\hline
2MASS J1821 & 2015-12-31 & 363 & 45 & 2MASS 18212622+1414064 \\
2MASS J0835 & 2016-06-25 & 352 & 60 & 2MASS 08354383-0819212 \\
\end{tabular}
\end{center}
\tablenotetext{}{}
\end{table*}

We observed 2MASS J1821 and J0835 each for one night as part of a pilot program to explore a variety of brown dwarfs with different variability levels and atmospheric temperatures.
Table \ref{tab:obsParam} shows the observing parameters for each target including the integration time, number of integrations and reference star.

Wavelength calibrations were performed with a 0.3$\times$60\arcsec\ slit and an argon emission lamp.
We performed calibrations sequences of argon emission lamp spectra and flat fielding with the 3$\times$60\arcsec\ slit both before and after the brown dwarf time series to obtain information on the flat field and any flexure in the instrument with telescope orientation.

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
	\label{fig:specphot0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
	\label{fig:specphot1821}
	}
	\caption{Top Panels: The target stars' median raw spectrum compared with the reference star. The areas near 1.4 and 1.8 $\mu$m are contaminated by telluric water absorption. The reference stars are significantly higher temperatures. Bottom Panels: Dynamic spectrum of 2MASS J1821.}
	\label{fig:specphot}
\end{figure*}

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Phase folded time series for both systems.}
	\label{fig:tserPfold}
\end{figure*}
